---
title: "Nile Tower Coverage Analysis"
format: html
editor: visual
execute:
  echo: false
---

```{r}
# Cargar librerías necesarias
library(leaflet)
library(readxl)
library(openxlsx)
library(sf)
library(ggplot2)
library(dplyr)
library(units)
library(giscoR)
library(scales)
library(plotly)

# Cargar y preparar datos
df2 <- read.csv("C:/Users/marc/Desktop/UOC/DataViz/P2/Africa towers.csv")
df_egypt <- df2[df2$Country == "Egypt", ]
df_egypt <- df_egypt[df_egypt$LON >= 30.6 & df_egypt$LON <= 33.2, ]
df_egypt <- df_egypt[, !(names(df_egypt) %in% c("created", "updated", "averageSignal", "Continent"))]

# Cargar gráficos desde archivo externo
source("plots.R")
```

------------------------------------------------------------------------

## Introduction

This report analyzes the cellular tower coverage along the Nile River in Egypt using geospatial data. Interactive visualizations have been created to explore tower range, radio technology, network providers, and spatial distribution. The result is an intuitive dashboard that helps evaluate actual network coverage around the Nile corridor. The part of interest of the route goes from Cairo to Aswan.

## Towers by Coverage Range

This bar chart shows the number of towers grouped by their approximate coverage range (in meters).

```{r}
plot_rango
```

------------------------------------------------------------------------

## Percentage of Towers by Radio Technology

This visualization displays the proportion of towers by radio technology (e.g., GSM, LTE, UMTS).

```{r}
plot_radio
```

------------------------------------------------------------------------

## Top 10 CIDs with Most Towers

Each CID represents a Base Transceiver Station (BTS) or sector. This chart highlights the top 10 CIDs with the most tower entries, which may indicate densely populated or technically redundant areas.

```{r}
plot_cid
```

------------------------------------------------------------------------

## Percentage of Towers by Network Operator

This chart shows the distribution of towers by network operator (e.g., Vodafone, Etisalat, Orange).

```{r}
plot_network
```

## Interactive Maps by Network

Each map below shows the towers deployed by a specific operator. The circles represent each tower's coverage radius, allowing a visual comparison of network reach across regions.

-   [Cell Towers Etisalat](tower_map_etisalat)

-   [Cell Towers Vodafone](tower_map_Vodafone)

-   [Cell Towers Orange](tower_map_Orange)

-   [Cell Towers WE](tower_map_WE)

## Interactive Maps by Radio Type

These maps classify towers by radio transmission type. Larger circles indicate towers with ranges exceeding 5 km. Each layer gives a detailed view of coverage by technology.

-   [GSM Coverage Map](map_radio_GSM)

-   [LTE Coverage Map](map_radio_LTE)

-   [NR Coverage Map](map_radio_NR)

-   [UMTS Coverage Map](map_radio_UMTS)

## Uncovered Areas

The following maps highlight the areas within 10 km of the Nile River that are not covered by any tower, segmented by radio technology:

-   [General Map Coverage](map_coverage)

## Conclusion

This visual analysis provides insight into the spatial distribution and technological composition of telecom infrastructure all along the Nile river in Egypt, going from Cairo to Aswan.
